Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-14 Presentation/gpm_november2016_vianello.tex
Include COMPASS into presentation

@@

\begin{frame}{Modelling require}
  \begin{enumerate}
    \item Mean field modelling available for AUG (EMC3-EIRENCE) and
      MAST-U (SOLPS). So far we lack investigation for these scenario
      targeting TCV. Manpower needed from edge and SOL modelling
    \item Turbulence code: we should need self-consistent interaction
      with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
      \texttt{GBS}. Some of them can be run by people who will, very
      likely, apply for this topic, some other not
  \end{enumerate}
\end{frame}

>>>>

\begin{frame}{COMPASS collaboration}
\begin{itemize}
\item COMPASS is not an MST1 device, therefore no operational cost
  will be provided by MST1
\item However GA agree that MST1 can provide part of the ppy for
  running experiments in line with MST1 topics
\item Proposal \# 14 is focused filaments dynamics and shoulder
  formation both in L and H-Mode
\item Experimental plan can be therefore agreed in order to perform
  similar experiments (e.g. I$_p$ and $q_{95}$ scan in L-Mode)
  ensuring proper comparison between devices
\item COMPASS suppose 3ppy for running and evaluation of experiment
  pertaining Topic-21, among Czeck and other european laboratories.
\end{itemize}
\end{frame}

@@

\begin{frame}{Modeling require}
  \begin{enumerate}
    \item Mean field modelling available for AUG (EMC3-EIRENCE) and
      MAST-U (SOLPS). So far we lack investigation for these scenario
      targeting TCV. Manpower needed from edge and SOL modelling
    \item Turbulence code: we should need self-consistent interaction
      with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
      \texttt{GBS}. Some of them can be run by people who will, very
      likely, apply for this topic, some other not
  \end{enumerate}
\end{frame}
